Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-22 paper/paper.tex
Ewa's edits to abstract and contributions

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new important problem of maximizing the number of
completed workflows from an ensemble under both budget and deadline constraints
on the Infrastructure-as-a-Service (IaaS) clouds, characterized by dynamic
resource provisioning capabilities and pay-per-use model.  We discuss, develop
and assess algorithms based on static and dynamic strategies for both task
scheduling and resource provisioning. We evaluate the algorithms via simulation
using a set of scientific workflow ensembles with a broad range of budget and
deadline parameters. This allows to identify the application scenarios and
constraint ranges for which the algorithms perform better. We found that the key
for algorithm performance is the decision which workflows should be admitted or
rejected from the ensemble. The results show that the admission procedure based
on worklfow structure and estimates of task runtimes can significantly improve
the quality of solutions.

@@

The main contributions of this paper are:
\begin{itemize}
  \item definition of the scheduling problem of priorotized workflows grouped in
  ensembles, under both budget and deadline constraints,
  \item analysis of static and dynamic strategies for task scheduling and
  resource provisioning on clouds, together with the admission procedure to
  predict which workflows from the ensemble can be completed,
  \item development of static and dynamic algorithms and of the simulator based
  on the defined application and infrastructure model,
  \item performance evaluation of algorithms on the set of synthetic benchmark
  workflow ensembles representing important real scientific applications,
  \item analysis of results, which allows to assess the advantages and
  disadvantages of proposed algorithms, depending on application scenarios and
  varying constraint values.
\end{itemize}

>>>>

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new important problem of efficiently managing such
ensembles under both budget and deadline constraints on the
Infrastructure-as-a-Service (IaaS) clouds. The latter are characterized by
dynamic resource provisioning capabilities and a pay-per-use model.  We discuss,
develop and assess algorithms based on static and dynamic strategies for both
task scheduling and resource provisioning. We assume that the workflows within
an ensemble are prioritized by the user. We evaluate the algorithms via
simulation using a set of scientific workflow ensembles with a broad range of
budget and deadline parameters. This allows to identify the application
scenarios and constraint ranges for which the algorithms perform better. We
found that the key for algorithm performance is the decision which workflows
within an ensemble should be admitted or rejected for execution. The results
show that the admission procedure based on workflow structure and estimates of
task runtimes can significantly improve the quality of solutions.

@@

The main contributions of this paper are:
\begin{itemize}
  \item the definition of the scheduling problem of prioritized workflows grouped in
  ensembles, under both budget and deadline constraints,
  \item an analysis of static and dynamic strategies for task scheduling and
  resource provisioning on clouds, together with the admission procedure to
  predict which workflows from the ensemble can be completed,
  \item the development of static and dynamic algorithms and of the simulator based
  on the defined application and infrastructure model,
  \item performance evaluation of algorithms on the set of synthetic benchmark
  workflow ensembles representing important real scientific applications,
  \item analysis of results, which allows to assess the advantages and
  disadvantages of proposed algorithms, depending on application scenarios and
  varying constraint values.
\end{itemize}
